---
title: "Your title"
author: "Your name"
date: "Your date"
output:
  xaringan::moon_reader:
    css: [default, maynooth, maynooth-fonts]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

```{r, eval=FALSE, echo=FALSE}
# Make sure you use the xaringan version 
# from github, so it has the maynooth template ------------------------
devtools::install_github("brunaw/xaringan")
```


class: inverse, middle, center

# A title slide

Text

---
class: middle, center

## Another title slide

Text

---

# First slide

More text here

- Bullet points
  - 'Sub' bullet points
  
1. Numbered topics

> Highlighting something

# Big
## Not so big
### Now is small


---

# Second slide


.pull-left[

- This is on the left side

]

.pull-right[
- While this is on the right side
]

### Inserting images

Use the following R code: 
  
```{r, out.width="85%", fig.align='center', echo = TRUE, eval=FALSE}
knitr::include_graphics("path/to/your/image")
```

  - Note that figure width and height are specified in
  chunk options, as 'out.width' and 'out.height'


Highlightning code:

    `r ''````{r tidy=FALSE}
    if (TRUE) {
    *{{ message("Very important!") }}
    }
    ```
---

## Third slide

1. This might be in a footnote *;

.footnote[[*] Not really. ]

Math expression: $$y_i \sim N(\mu, \sigma^{2})$$

Tables:
```{r, echo = TRUE}
knitr::kable(head(iris), format = 'html')
```

---

## Fourth slide

You can find more features by
1. Creating a `rmarkdown` file 
2. Selecting the xaringan theme for it: the example document
comes with instructions about how to use it!


---

# References

```{r, refs, results='asis', echo=FALSE, warning=FALSE, message=FALSE}
source('references.R')

# Selecting some references
references(bib_file = 'scholar.bib', select = TRUE, 
           keys = c('friedman2008sparse', 'rowley1998neural'))

# Or printing it all
references(bib_file = 'scholar.bib', select = FALSE)
```

---

class: center, middle

# Thanks!



